### 2016-01-20 paper.tex
Add point about scale threshold for numerical model validation
Near wake velocity was measured

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
mean kinetic energy transport were compared with results from a high solidity
turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 case---a consequence of
both the relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. The effects of blade support strut drag on turbine performance
were investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced the rotor power coefficient.
Strut drag was also measured for the NACA 0021 and cylindrical configurations
with the blades removed.

@@

The performance and near-wake of a 1:6 scale DOE Reference Model 2 cross-flow
turbine was measured in a towing tank.

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynolds number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades.

>>>>

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed
ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured
at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence kinetic energy, and
mean kinetic energy transport were compared with results from a high solidity
turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 case---a consequence of
both the relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. The effects of blade support strut drag on turbine performance
were investigated by covering the rotor's NACA 0021 struts with cylinders. As
expected, this modification drastically reduced the rotor power coefficient.
Strut drag was also measured for the NACA 0021 and cylindrical configurations
with the blades removed.

@@

The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
cross-flow turbine was measured in a towing tank.

Performance was assessed for Reynolds number dependence, showing a convergence
to a weakly $Re$-dependent linear regime at approximately $Re_D \approx 1 \times
10^6$ or $Re_{c,\mathrm{ave}} \approx 2 \times 10^5$. Comparison was made
between this turbine and the higher solidity UNH-RVAT, tested in nearly
identical conditions, which showed similar Reynolds number thresholds but a
flatter linear regime, likely to due virtual camber of the higher
chord-to-radius ratio of the UNH-RVAT blades. Nevertheless, these results
indicate an important transitional scale threshold beyond which data should be
taken for numerical model validation, in order to stay relevant to full scale
devices.
